Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-14 prob.tex
prob.tex \section{Proofs} Fix the definition...

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ or
$f:\mathbb{C}S^{d-1}\rightarrow\mathbb{R}$ is called a \emph{real}
or \emph{complex approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if
\begin{itemize}
\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$ or $\mathbb{C}^{d}$.
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in S^{d-1}$ and $\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $
or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
\end{itemize}
Also, we will use the same letter $f$ to denote the function defined
on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$and
$f\left(0\right)=0$~\cite{RichmanBridges1999}.\qed\end{definition}

>>>>

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ or
$f:\mathbb{C}S^{d-1}\rightarrow\mathbb{R}$ is called a \emph{real}
or \emph{complex approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if
\begin{itemize}
\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$ or $\mathbb{C}^{d}$.
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in S^{d-1}$ or $\ket{\psi}\in\mathbb{C}S^{d-1}$ and
$\lambda\in S^{0}$ or $\lambda\in\mathbb{C}S^{0}$.
\end{itemize}
Also, we will use the same letter $f$ to denote the function defined
on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$and
$f\left(0\right)=0$~\cite{RichmanBridges1999}. In this case, 
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{R}^{d}$ or $\ket{\psi}\in\mathbb{C}^{d}$ and
$\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $ or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
\end{itemize}
\qed\end{definition}
